---
title: "Project 3 Part 2 Analysis"
author: "Alexander Thomson"
date: "06/10/2021"
output: html_document
---

<!--- Begin styling code. --->
<style type="text/css">
/* Whole document: */
body{
  font-family: "Palatino Linotype", "Book Antiqua", Palatino, serif;
  font-size: 12pt;
}
h1.title {
  font-size: 38px;
  text-align: center;
}
h4.author {
  font-size: 18px;
  text-align: center;
}
h4.date {
  font-size: 18px;
  text-align: center;
}
</style>
<!--- End styling code. --->

```{r, message = FALSE}
library(tidyverse)
library(ggplot2)
library(randomForest)
library(kableExtra)
```

# Data

```{r}
# load the my_rf_cv function
source("../Code/my_rf_cv.R")

# load in the data sets in the Data folder
my_gapminder <- read.csv("../Data/my_gapminder.csv")
my_penguins <- read.csv("../Data/my_penguins.csv")
```

```{r}
# create the matrix to store all the simulated MSEs
my_cv_MSEs <- matrix(NA, nrow = 30, ncol = 3)
counter <- 1
for (k in c(2, 5, 10)) {
  k_MSE <- c()
  for (i in 1:30) {
    k_MSE[i] <- my_rf_cv(k)
  }
  # store the 30 simulated values for this k in its own row of the overall matrix
  my_cv_MSEs[, counter] <- k_MSE
  counter <- counter + 1
}
# the matrix of the generated average MSEs
head(my_cv_MSEs)
```

# Figures

In the code below we generate and save three boxplots of the 30 average MSEs we generated in the section above.

```{r, warning = FALSE, message = FALSE}
k2_cv_MSEs <- data.frame("MSE" = my_cv_MSEs[, 1])
k2_box_plot <- ggplot(data = k2_cv_MSEs, aes(x = "", y = MSE)) +
  geom_boxplot(fill = "lightblue") +
  theme_classic(base_size = 15) +
  labs(title = "A boxplot of the average MSE from k-fold cross validation \n of random forests run 30 times using k = 2",
       x = "k = 2", y = "Average MSE") +
  theme(plot.title = element_text(hjust = 0.5))
# save the k = 2 boxplot
ggsave(plot = k2_box_plot, filename = "k2_box_plot.png", path = "../Output/Figures")

k2_box_plot
```

```{r, warning = FALSE, message = FALSE}
k5_cv_MSEs <- data.frame("MSE" = my_cv_MSEs[, 2])
k5_box_plot <- ggplot(data = k5_cv_MSEs, aes(x = "", y = MSE)) +
  geom_boxplot(fill = "red") +
  theme_classic(base_size = 15) +
  labs(title = "A boxplot of the average MSE from k-fold cross validation \n of random forests run 30 times using k = 5",
       x = "k = 5", y = "Average MSE") +
  theme(plot.title = element_text(hjust = 0.5))
# save the k = 5 boxplot
ggsave(plot = k5_box_plot, filename = "k5_box_plot.png", path = "../Output/Figures")

k5_box_plot
```

```{r, warning = FALSE, message = FALSE}
k10_cv_MSEs <- data.frame("MSE" = my_cv_MSEs[, 3])
k10_box_plot <- ggplot(data = k10_cv_MSEs, aes(x = "", y = MSE)) +
  geom_boxplot(fill = "lightgreen") +
  theme_classic(base_size = 15) +
  labs(title = "A boxplot of the average MSE from k-fold cross validation \n of random forests run 30 times using k = 10",
       x = "k = 10", y = "Average MSE") +
  theme(plot.title = element_text(hjust = 0.5))
# save the k = 10 boxplot
ggsave(plot = k10_box_plot, filename = "k10_box_plot.png", path = "../Output/Figures")

k10_box_plot
```

# Summary Statistics

In this section, we create a table of summary statistics of the average MSEs for each value of $k$ and then save that table and the data frame of all the generated average MSEs to files in the Results folder.

```{r}
# create a table with each value of k and the corresponding summary statistics
my_MSE_table <- matrix(NA, nrow = 3, ncol = 3)

my_MSE_table[1, 1] <- 2
my_MSE_table[2, 1] <- 5
my_MSE_table[3, 1] <- 10

my_MSE_table[1, 2] <- mean(my_cv_MSEs[, 1])
my_MSE_table[2, 2] <- mean(my_cv_MSEs[, 2])
my_MSE_table[3, 2] <- mean(my_cv_MSEs[, 3])

my_MSE_table[1, 3] <- sd(my_cv_MSEs[, 1])
my_MSE_table[2, 3] <- sd(my_cv_MSEs[, 2])
my_MSE_table[3, 3] <- sd(my_cv_MSEs[, 3])

my_MSE_table <- data.frame(my_MSE_table)
colnames(my_MSE_table) <- c("k", "mean", "standard deviation")

# display the table
kable_styling(kable(my_MSE_table))
```

```{r}
# save the summary statistic table in the results folder of output
saveRDS(my_MSE_table, file = "../Output/Results/summary_stat_table.rds")

output_results <- data.frame(my_cv_MSEs)
colnames(output_results) <- c("k2", "k5", "k10")

# store the results in their own csv in the results folder of output
write_csv(output_results, file = "../Output/Results/simulated_results.csv")
```






